In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-24 paper/main.tex
Fix typo.
Updates from Overleaf

The software developed to generate and analyze the numerical results
of this study are openly available on Zenodo with the identifier doi:
10.5281/zenodo.14749163. In addition to simulation and analysis
software, this archive also includes surface triangulations used for
geometry representation, computational meshes (3D meshes and 1D
networks), segmentations, sample simulation outputs from the baseline
and high PVS flow models, and animations.

>>>>

The software developed to generate and analyze the numerical results
of this study is openly available on Zenodo with the identifier doi:
10.5281/zenodo.14749163. In addition to simulation and analysis
software, this archive also includes surface triangulations used for
geometry representation, computational meshes (3D meshes and 1D
networks), segmentations, sample simulation outputs from the baseline
and high PVS flow models, and animations.
